\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-27 papers/jfp/7-experience.tex
Use \Cloud \Shake consistently

\subsection{Experience from Cloud \Shake}\label{sec-cloud-shake}

Converting \Shake into Cloud \Shake wasn't a difficult process once armed with a roadmap. The key was the introduction of two new functions:

@@

\subsection{Experience from using Cloud \Shake}

While we expected the GHC build system to be the first to take advantage of Cloud \Shake, we were actually beaten to it by Standard Chartered who report\footnote{\url{https://groups.google.com/d/msg/shake-build-system/NbB5kMFS34I/mZ9L4TgkBwAJ}}:

@@

We have also got the GHC build working with Cloud \Shake, resulting in build times of N minutes instead of M minutes. Due to aspects like \hs{configure} we don't see the dramatic reductions reported by Standard Chartered. Converting to a build suitable for sharing is not overly onerous, but nor is it trivial. Some things that require attention:

>>>>

\subsection{Experience from \Cloud \Shake}\label{sec-cloud-shake}

Converting \Shake into \Cloud \Shake wasn't a difficult process once armed with a roadmap. The key was the introduction of two new functions:

@@

\subsection{Experience from using \Cloud \Shake}

While we expected the GHC build system to be the first to take advantage of \Cloud \Shake, we were actually beaten to it by Standard Chartered who report\footnote{\url{https://groups.google.com/d/msg/shake-build-system/NbB5kMFS34I/mZ9L4TgkBwAJ}}:

@@

We have also got the GHC build working with \Cloud \Shake, resulting in build times of N minutes instead of M minutes. Due to aspects like \hs{configure} we don't see the dramatic reductions reported by Standard Chartered. Converting to a build suitable for sharing is not overly onerous, but nor is it trivial. Some things that require attention:
